---
title: "top priority item pie charts"
author: "Naomi Liftman"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r message = FALSE, warning = FALSE, error = FALSE}
# loading the necessary libraries
library(tidyverse)
library(ggplot2)
library(rio)
library(stringr)
library(RColorBrewer)
library(gt)
library(gtExtras)
library(data.tree)
library(treemap)
library(dplyr)
library(ggrepel)
library(forcats)
library(scales)
```

# Teaching for top priority item 

```{r}
#pulling the data and just getting the qualitative responses 
survey_hopefully <- import("well_being_survey.xlsx") %>% 
  rename( "first_priority" = 17,
          "second_priority" = 18,
          "third_priority" = 19)

teaching_priority <- survey_hopefully %>% 
  select(first_priority:third_priority)
```

# Selecting just the first prirorites 

```{r}
#counting peoples top priorities 
teaching_df <- teaching_priority %>% 
  drop_na(first_priority) %>% 
  count(first_priority) 

#removing the rows that make no sense (are numbers)
teaching_df_clean <- teaching_df[-c(1:11, 21), ]

#adding percentages and only letting them go to 2 decimals
teaching_df_clean <- teaching_df_clean %>% 
  mutate(perc = (n/sum(n))*100) 
teaching_df_clean$perc <- round(teaching_df_clean$perc, digits = 2)

#rearranged for making pretty pie charts
teaching_pie <- teaching_df_clean %>% 
  arrange(desc(n))
```

# Graphing it baby
```{r}
ggplot(data = teaching_df_clean, aes(x = first_priority, y = n, fill = first_priority)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle= 45, hjust = 1)) +
  labs(x = "Item", y = "Count", title = "Top Priority in Teaching")  +
  scale_fill_manual(values = c("#e2c5e8", "#e2c5e8", "#e2c5e8", "#427a05", "#cbd563","#9bc563", "#e2c5e8", "#e2c5e8", "#e2c5e8"), guide = "none") 

```
# Making a Pie Chart
```{r}
pie(teaching_pie$n, 
    col = c("white", "white", "white", "#d929ee", "#9580F1","#11ceda", "white", "white", "white"),
    labels = c("Course release", "Mentoring for teaching", "Other", "Realistic faculty workloads", "Replace student evaluations", "Teaching resources", "Three-year teaching schedule", "Training for mentoring graduate students","Upgrade technology"),
    main = "Top Priority in Teaching")
```

# making a much hotter and cooler pie chart
```{r}
ggplot(teaching_pie, aes(x = "", y = perc, fill = first_priority)) +
  geom_col(color = "black") +
  geom_label(aes(label = perc),
             position = position_stack(vjust = .5),
             show.legend = FALSE) +
  coord_polar(theta = "y") + 
  theme_void()+
  labs(title = "Top Priority in Teacing",
       fill = "Item of Top Priority") +
  scale_fill_manual(values = c("#f7fcf5", "#e5f5e0", "#c7e9c0", "#d929ee", "#9580F1","#11ceda", "#a1d99b", "#74c476", "#41ab5d"))
```

# again trying to make it easier to read
```{r}
#cannot figure out how to reorder a pie chart if I do it this way?
#may just need to do a pie chart function and go crazy with that

#god this is ugly goddamn
pie(teaching_pie$n, labels = teaching_pie$perc, col = rainbow(length(teaching_pie$first_priority)))
legend("topright", c("Realistic faculty workloads","Teaching resources", "Replace student evaluations", "Upgrade technology", "Other", "Training for mentoring graduate students", "Course release", "Mentoring for teaching", "Three-year schedule"), cex = 0.5, fill = rainbow(length(teaching_pie$first_priority)))

# ahhhhhh
ggplot(teaching_df_clean, aes(x = "", y = perc, fill = first_priority)) +
  geom_col(color = "black") +
  coord_polar(theta = "y")
  
```



# attempting to make the pie chart easier to read!

```{r}
#this tragically does not work and is indeed ugly

#ggplot(teaching_df_clean, aes(x = "", y = perc, fill = first_priority)) +
 #      geom_bar(width = 1, stat = "identity") +
  #     coord_polar("y", start = 0) +
   #    geom_label_repel(aes(label = perc), size=5, show.legend = F, nudge_x = .7, nudge_y = -1) +
    #   guides(fill = guide_legend(title = "Group"))
```



# Selecting second priorities

```{r}
#counting peoples top priorities 
teaching_df_two <- teaching_priority %>% 
  drop_na(second_priority) %>% 
  count(second_priority) 

#removing the rows that make no sense (are numbers)
teaching_df_clean_two <- teaching_df_two[-c(1:11, 21), ]
```

# Graphing it baby
```{r}
ggplot(data = teaching_df_clean_two, aes(x = second_priority, y = n, fill = second_priority)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle= 45, hjust = 1)) +
  labs(x = "Item", y = "Count", title = "Top Priority in Teaching") + 
  scale_colour_brewer(palette = 1)

```
# Selecting third priorities

```{r}
#counting peoples top priorities 
teaching_df_three <- teaching_priority %>% 
  drop_na(third_priority) %>% 
  count(third_priority) 

#removing the rows that make no sense (there are for some reason a lot on this one)
teaching_df_three_clean <- teaching_df_three %>% 
  filter(n != 1)
```

# Graphing it baby
```{r}
ggplot(data = teaching_df_three_clean, aes(x = third_priority, y = n, fill = third_priority)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle= 45, hjust = 1)) +
  labs(x = "Item", y = "Count", title = "Top Priority in Teaching") + 
  scale_colour_brewer(palette = 1)

```

# Merging the dataframes
```{r}
#renameing the n to the count for the top choice
teaching_df_clean <- teaching_df_clean %>% 
  rename("count_first" = n)

#renaming the n to the count for the second choice
teaching_df_clean_two <- teaching_df_clean_two %>% 
  rename("count_second" = n)

#joining them!!!!
by <- join_by(first_priority == second_priority)
top_two <- full_join(teaching_df_clean, teaching_df_clean_two, by)

#adding our final group horray!!!
teaching_df_three_clean <- teaching_df_three_clean %>% 
  rename("count_third" = n)

by_part_two = join_by(first_priority == third_priority)
top_tree <- full_join(top_two, teaching_df_three_clean, by_part_two)

```


# Creating Pretty tables from the data frame
```{r}
#initializing as a gt
table_1 <- gt(top_tree)

#now making it pretty
table_1_part_2 <- table_1 %>% 
  cols_label(
    first_priority = "",
    count_first = "1st",
    count_second = "2nd",
    count_third = "3rd") %>% 
    gt_add_divider(columns = c(first_priority, count_first, count_second)) %>% 
  cols_align(
  align = c("center"),
  columns = c(count_first, count_second, count_third)) %>% 
  gt_highlight_rows(
    columns = c(count_first, count_second),
    rows = c(4), 
    font_weight = "normal") %>% 
  gt_highlight_rows(
    columns = c(count_third),
    rows = c(5), 
    font_weight = "normal")

table_1_part_2
```

# Messing with the data now
```{r}
#renameing the n to the count for the top choice
#teaching_df_clean <- teaching_df_clean %>% 
#  rename("count_first" = n)

#renaming the n to the count for the second choice
#teaching_df_clean_two <- teaching_df_clean_two %>% 
#  rename("count_second" = n)

#merging the two
#top_twooo <- teaching_df_clean %>% 
#  cross_join(teaching_df_clean_two)

#renaming the third
#teaching_df_clean_threeee <- teaching_df_three_clean %>% 
#  rename("count_third" = 2)

#merging all three 
#top_threee <- top_twooo %>% 
#  cross_join(teaching_df_clean_threeee)
```

#graphing it?
```{r}
ggplot() + 
  geom_col(data = top_tree, aes(x = first_priority, y = count_first, fill = "red")) +
  theme(axis.text.x = element_text(angle= 45, hjust = 1)) +
  geom_col(data = top_tree, aes(x = first_priority, y = count_second, fill = "blue")) +
  geom_col(data = top_tree, aes(x = first_priority, y = count_third, fill = "green")) 
```




