---
title: "qualitative measures of teaching"
author: "Naomi Liftman"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r message = FALSE, warning = FALSE, error = FALSE}
# loading the necessary libraries
library(tidyverse)
library(ggplot2)
library(rio)
library(stringr)
library(RColorBrewer)
library(gt)
library(gtExtras)
```

# First Section Qualitative Analysis

```{r}
#pulling the data and just getting the qualitative responses 
survey_hopefully <- import("qualitative_well_being.csv") %>% 
  rename("teaching" = 16,
         "gov" = 32,
         "worklife" = 47,
         "research" = 61)

qualitative <- survey_hopefully %>% 
  select(teaching, gov, worklife, research)
```

#starting the cleaning for teaching
```{r}
#counting everything for teaching
qualitative %>% count(teaching)

#manually changing the silly ones 
#update tech
qualitative[qualitative == "Update Tech"] <- "Upgrade Tech"
qualitative[qualitative == "Upgrade tech"] <- "Upgrade Tech"
qualitative[qualitative == "Embrace Technology"] <- "Upgrade Tech"

# Teaching Culture
qualitative[qualitative == "Teaching Culture"] <- "Teaching Excellence"

#Pedagogical Skills
qualitative[qualitative == "Pedagogical Skills"] <- "Pedagogy Skills"

# online teaching
qualitative[qualitative == "Online Teaching"] <- "Hybrid Teaching"

# mentorship
qualitative[qualitative == "Incentives for Mentorship"] <- "Incentives for Mentoring"

# FTE
qualitative[qualitative == "FT Teaching"] <- "FTE"

#counting everything for teaching after changing
qualitative %>% count(teaching)
```
# Pretty Tables for Teaching
```{r}
#just teaching
teaching <- qualitative %>% 
  select(teaching) %>% 
  count(teaching)

#removing all of the blanks
teaching <- teaching[-c(1), ]

#selecting only things that have more than 1! 
teaching_more <- teaching %>% 
  filter(n > 1)

#initializing as a gt
table_1 <- gt(teaching)
#showing it
table_1

#initialize over 2 as a gt 
table_2 <- gt(teaching_more)
#showing it
table_2

#teaching over 3
teaching_3 <- teaching %>% 
  filter(n > 2)
table_3 <- gt(teaching_3)
table_3
```

# side by side tables
```{r}
#picking first half manually
first_half_teaching <- teaching_more %>% 
  slice(1:19)

#picking second half manually
second_half_teaching <- teaching_more %>%
  slice(20:38)

#converting to GT tables
first_half_teaching <- gt(first_half_teaching)
#adding highlighting
first_half_teaching <- first_half_teaching %>%
  #i am going to manually fill in each column like a PSYCHO <3 
  data_color(columns = n,
             target_columns = c(teaching, n),
             color = "#AED6F1",
             rows = c(3, 8, 10, 13, 14, 18)) %>% 
  data_color(columns = n,
             target_columns = c(teaching, n),
             color = "#5DADE2",
             rows = c(1,2)) %>% 
  data_color(columns = n,
             target_columns = c(teaching, n),
             color = "#2E86C1",
             rows = c(5, 12, 15, 19, 17)) %>% 
  data_color(columns = n,
             target_columns = c(teaching, n),
             color = "#1B4572",
             rows = c(4, 6, 7, 9, 11, 16)) %>% 
  gt_highlight_rows(fill = "#C0392B",
                    rows = c(6))
  
    #hrmmmmm not sure I like the highlights, so I'm going to do it once with 
  #highlight and once with just colored in
 #yeah I actually hate the highlight going to do the colored in! so fun
  #gt_highlight_rows(rows = c(3, 8, 10, 13, 14, 18),
   #                 fill = "#AED6F1") %>% 
  #gt_highlight_rows(rows = c(1, 2),
    #                fill = "#5DADE2")
  #gt_highlight_rows(
   # columns = c(teaching, n),
    #rows = c(4, 6, 16), 
    #font_weight = "normal")
  
#converting to GT tables
second_half_teaching <- gt(second_half_teaching)
#adding highlighting
second_half_teaching <- second_half_teaching %>% 
  data_color(columns = n,
             target_columns = c(teaching, n),
             color = "#AED6F1",
             rows = c(2,3,16 )) %>% 
  data_color(columns = n,
             target_columns = c(teaching, n),
             color = "#5DADE2",
             rows = c(1,5,9, 7,18)) %>% 
  data_color(columns = n,
             target_columns = c(teaching, n),
             color = "#2E86C1",
             rows = c(6, 8, 10,11,14)) %>% 
  data_color(columns = n,
             target_columns = c(teaching, n),
             color = "#1B4572",
             rows = c(12,13,15, 17,19)) %>% 
  gt_highlight_rows(fill = "#C0392B",
                    rows = c(4,19))

#adding them to a list
listed_tables <- list(first_half_teaching, second_half_teaching)

#making into a pretty table!
gt_two_column_layout(listed_tables) 
```

# Main take away from TEACHING:
People want to see Pay (38), Workload (26), and Clinical (18)

# The other sections
## Gov
```{r}
#taking all the gov things
government <- survey_hopefully %>% 
  select(gov)

#looking at counts for gov
government %>% 
  count(gov)

#these are the top BY FAR 
#pay 37
#pay gap 24
#reduce admin bloat 28
```


## Worklife
```{r}
work <- survey_hopefully %>% 
  select(worklife)

work %>% 
  count(worklife)

#cultural changes 16
#free tuition for families 12
#pay 13
#safe buildings 13
#childcare 9
```

# Research
```{r}
research <- survey_hopefully %>% 
  select(research)

#count
research %>% 
  count(research)

#arts 32
#grants 29
#workday 9
#funding 9
```

#adding them all together like a crazy person to see totals
#this was actually the completly wrong way to do it hahahaha
```{r}
#the columns gotta be the same so gonna rename them!
#teaching
teaching <- teaching %>% 
  rename("item" = teaching)

#government, get counts and rename
gov <- government %>% 
  count(gov) %>% 
  rename("item" = gov)
#removing all of the blanks
gov <- gov[-c(1), ]

#worklife
work <- work %>% 
  count(worklife) %>% 
  rename("item" = worklife)
#removing all of the blanks
work <- work[-c(1), ]

#research
research <- research %>% 
  count(research) %>% 
  rename("item" = research)
#removing all of the blanks
research <- research[-c(1), ]

#combining them all
all_qual <- rbind(teaching, gov)
all_qual <- rbind(all_qual, work)
all_qual <- rbind(all_qual, research)
```

# haha now doing it correctly like a fools
```{r}
#just t
t <- survey_hopefully %>% 
  select(teaching) %>% 
  rename("item" = teaching)

g <- survey_hopefully %>% 
  select(gov) %>% 
  rename("item" = gov)

worklife <- survey_hopefully %>% 
  select(worklife) %>% 
  rename("item" = worklife)

research <- survey_hopefully %>% 
  select(research) %>% 
  rename("item" = research)

#all of em!!! horrayYYYYyyYyY
qualitative_all <- bind_rows(t, g, worklife, research)

#remove all the rows without anything in them
q_all_no_empty <- data.frame(qualitative_all[!apply(qualitative_all == "", 1, all),])

#rename bc what the hell happened
q_all_no_empty <- q_all_no_empty %>% 
  rename("item" = 1)

#fixing all these goddamn shits by hand before counting them
q_all_no_empty[q_all_no_empty == "Core resources"] <- "Core Resources"
q_all_no_empty[q_all_no_empty == "Culture"] <- "Cultural Changes"
q_all_no_empty[q_all_no_empty == "Culture Changes"] <- "Cultural Changes"
q_all_no_empty[q_all_no_empty == "Dean Accountability"] <- "Accountability"
q_all_no_empty[q_all_no_empty == "Department Chair Accountability"] <- "Accountability"
q_all_no_empty[q_all_no_empty == "Housing Assistance"] <- "Housing"
q_all_no_empty[q_all_no_empty == "Incentives for Mentorship"] <- "Incentives for Mentoring"
q_all_no_empty[q_all_no_empty == "Pedagogical Skills"] <- "Pedagogy Skills"
q_all_no_empty[q_all_no_empty == "Sabbatical"] <- "Sabbatical for Teaching Track"
q_all_no_empty[q_all_no_empty == "Student Harrassment"] <- "Student Harassment"
q_all_no_empty[q_all_no_empty == "TA support"] <- "TA Support"
q_all_no_empty[q_all_no_empty == "Tri-Campus Structure"] <- "Tri-Campus"
q_all_no_empty[q_all_no_empty == "Upgrade tech"] <- "Upgrade Tech"
q_all_no_empty[q_all_no_empty == "Workloads"] <- "Workload"
q_all_no_empty[q_all_no_empty == "Accountability for Tenure Track Faculty"] <- "Accountability"
q_all_no_empty[q_all_no_empty == "Accountability for Tenure Faculty"] <- "Accountability"
q_all_no_empty[q_all_no_empty == "Pay Gap"] <- "Pay"



#getting the counts
q_n <- q_all_no_empty %>% 
  count(item)

#taking all the ones with over 4
#that gives me  56 items (too many i could do like 20)
q_n_4 <- q_n %>% 
  filter(n >= 4)

#doing over 5 (haha only 51)
q_n_5 <- q_n %>% 
  filter(n >= 5)

#(down to 35)
q_n_6 <- q_n %>% 
  filter(n > 5)

#now over 10
q_n_10 <- q_n %>% 
  filter(n > 9)
```

# making a sexy little table <3 
```{r}
#picking first half manually
first_q <- q_n_10 %>% 
  slice(1:11)

#picking second half manually
second_q <- q_n_10 %>% 
  slice(12:22)

#converting to GT tables
first_q_gt <- gt(first_q)
#adding highlighting
first_q_gt <- first_q_gt %>% 
  gt_highlight_rows(rows = c(9))

second_q_gt <- gt(second_q)
second_q_gt <- second_q_gt %>% 
  gt_highlight_rows(rows = c(2, 10))

#adding them to a list
listed_tables <- list(first_q_gt, second_q_gt)

#making into a pretty table!
gt_two_column_layout(listed_tables) 
```


